ActiveCA: Time Use Data from the General Social Survey of Canada to Study Active Travel

### 2024-12-14 paper/Manuscript-Data-Package.Rmd
Upload new version with adjusting of the weights for the 1992 survey

<!-- 
FROM THE ABSTRACT:

The package also details the respondent's region characteristics, specifying wheter they live in a metropolitan area and their province of residency. {ActiveCA} also provides pre-estimated impedance functions for active travel for Canadian Metropolitan Area and Census Agglomerations, which can be used in accessibility analysis to calculate the cost of travel between different locations. The package will continue to expand with contributions from the authors and the broader community through requests in the future. {ActiveCA} is freely accessible for exploration and download from the associated Github repository, where the documentation and code involved in creating and manipulating data are detailed.
-->

@@

```{r load-data, include = FALSE}
# Load data
data("gss_episodes")
data("gss_impedances")
data("gss_main_2015")

# Original main and episode files from 2015 to display table examples

gss_m_2015 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2015/gss-m.csv"))
gss_e_2015 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2015/gss-e.csv"))

@@

>>>>

@@

```{r load-data, include = FALSE}
# Load data
data("gss_episodes")
data("gss_impedances")

# Original main and episode files from 2015 to display table examples
gss_m_2015 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2015/gss-m.csv"))
gss_e_2015 <- read.csv(paste0(here(), "/data-raw/source-files/Time-use-2015/gss-e.csv"))

@@

`ActiveCA` also provides a Jupyter Notebook containing a Python script that demonstrates how to read R data files (.rda) and convert them into Pandas DataFrames. This process allows users to work with and utilize the datasets available in `ActiveCA` within a Python project.
